Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population

### 2023-11-10 analysis/paper/paper.tex
update NEWS.md

\newgeometry{top=30mm,left=30mm}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

All raw data is available on Zenodo
(\url{https://doi.org/10.5281/zenodo.8061483}). Analysis scripts, and
the source code for the manuscript and supplementary materials are
available as a research compendium
(\url{https://doi.org/10.5281/zenodo.7649825}) using the structure
recommended by the \textbf{rrtools} R package (Marwick, 2019).

>>>>

\newgeometry{top=30mm,left=30mm}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, interior hidden, sharp corners, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

All raw data is available on Zenodo
(\url{https://doi.org/10.5281/zenodo.8061483}). Analysis scripts, and
the source code for the manuscript and supplementary materials are
available as a research compendium
(\url{https://doi.org/10.5281/zenodo.7649824}) using the structure
recommended by the \textbf{rrtools} R package (Marwick, 2019).
